Combining information from photometric and spectroscopic data:\\ propogating uncertainties in spectrophotometric calibration

### 2015-04-27 tex/figures.tex
new figure captions, untrack all old figures

\begin{figure}[h!]
%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
\caption{The calibrated spectrum for \excluster, along with the
uncertainties (bottom panel).The right panel shows the
spectrophotometric calibration vector determined by
\citet{schiavon05}. \label{fig:ggc_data}}
\end{figure}

\begin{figure}[h!]
%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
\caption{A mock spectrum for a star cluster with $10^5 M_\odot$ total
  stellar mass, an age of  9 Gyr, solar
  metallicity, and $A_V=0.5$ mag. \label{fig:mock_data}}
\end{figure}

@@

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from an \emph{uncalibrated} mock
  spectrum and a single photometric data point.
Top Left: The observed spectrum. The mock observed spectrum ({\it
black}) is shown as well as YY model spectra constructed from draws
from the posterior PDFs of the model parameters, including calibration
parameters {\it green}.
Bottom Left: The calibration vector. The true calibration vector ({\it
black}) that was used to construct the mock spectrum is compared to
posterior samples of the inferred calibration vector ({\it green})
which include both the polynomial and the Gaussian Process mean
prediction (Equation
\ref{eq:calibration}).
Top Right: The intrinsic spectrum. Samples of the posterior prediction
for the \emph{intrinsic} spectrum ({\it green}) as well as for the
photometry ({\it magenta}).  The true mock photometry is also shown
({\it black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:speconly_calibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from the photometry only.
Top: The intrinsic spectrum. Samples of the posterior prediction
for the \emph{intrinsic} spectrum ({\it green}) as well as for the
photometry ({\it magenta}).  The true mock photometry is also shown
({\it black}).
Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:speconly_calibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from the combination of mock 
Top Left: The observed spectrum. The mock observed spectrum ({\it
black}) is shown as well as YY model spectra constructed from draws
from the posterior PDFs of the model parameters, including calibration
parameters {\it green}.
Bottom Left: The calibration vector. The true calibration vector ({\it
black}) that was used to construct the mock spectrum is compared to
posterior samples of the inferred calibration vector ({\it green})
which include both the polynomial and the Gaussian Process mean
prediction (Equation
\ref{eq:calibration}).
Top Right: The intrinsic spectrum. Samples of the posterior prediction
for the \emph{intrinsic} spectrum ({\it green}) as well as for the
photometry ({\it magenta}).  The true mock photometry is also shown
({\it black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:speconly_calibrated}}
\end{figure*}

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics[width = 0.5 \textwidth]{figures/data.pdf}
\caption{Observational data. 
Top: The calibrated spectrum for \excluster.
Middle: The signal-to-noise ratio.
Bottom: The spectrophotometric calibration vector determined by
\citet{schiavon05}. Note the wiggles in the calibration vector\label{fig:ggc_data}}
\end{center}
\end{figure}

\begin{figure}[h!]
%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
\caption{A mock spectrum for a star cluster with the fiducial
parameters $10^5 M_\odot$ total stellar mass, an age of 9 Gyr, solar
metallicity, and $A_V=0.5$ mag. \label{fig:mock_data}}
\end{figure}

@@

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from an \emph{uncalibrated} mock
  spectrum and a single photometric data point.  Panels and colors are
  as in Figure \ref{fig:speconly_calibrated}.  In this case the
  observed spectrum is in arbitrary units and the true
  calibration vector is not a constant with wavelength.
\label{fig:speconly_uncalibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from the photometric data only.
Top: The intrinsic spectrum. Samples of the posterior prediction
for the \emph{intrinsic} spectrum ({\it green}) and the
photometry ({\it magenta}).  The mock photometry is also shown
({\it black}).
Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:photonly}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from the combination of
  \emph{uncalibrated} spectroscopy and all the photometric data
  points.  Panels and colors are as in Figure \ref{fig:speconly_calibrated}.
\label{fig:speconly_calibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Joint posterior PDFs for several physical parameters. The
  posteriors obtained from photometry only is in {\it red}, from
  \emph{uncalibrated} spectroscopy and a single photometric point in {\it blue}, and from
  the photometry and spectroscopy combined in {\it magenta}.
\label{fig:combined_posterior}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Posterior PDFs obtained from multiple noise realizations of the
  mock photometry and uncalibrated spectra, for a single set of
  parameters.  The input mock parameters are shown as a 
  vertical line, medians of the posterior CDF for each realization are
  shown as dotted lines.
\label{fig:noise_realizations}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Posterior PDFs obtained from mock spectra and photometry
  created with  a variety of mock physical parameters, as a function
  of those parameters.
\label{fig:mock_parameter_space}}
\end{figure*}

### 2015-04-27 tex/ms.tex
new figure captions, untrack all old figures

\item Mock perfectly calibrated data: inference using spectroscopy and all
  photometry, with both full calibration model and assuming no
  calibration uncertainty.

@@

Our strategy is easily extensible to more complicated models, which
include for example night sky-line emission in the spectroscopy (or
residuals from an intial sky-line subtraction) and uncertainties in
wavelength calibration. Furthermore, more complex physical models may
be considered for the mean object model, for example including SFH
parameters so as to model galaxies.  {\color{blue} DISCUSS MORE
COMPLICATED COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL
CHECKING.}

@@

>>>>

\item Do this for a bunch of ages, metallicities, and dust
  attenuations, possibly compare to the ideal posteriors.

@@

Our strategy is easily extensible to more complicated models, which
include for example night sky-line emission in the spectroscopy (or
residuals from an intial sky-line subtraction) and uncertainties in
wavelength calibration \citep[e.g.,][]{walker15}. Furthermore, more complex physical models may
be considered for the mean object model, for example including SFH
parameters so as to model galaxies.  {\color{blue} DISCUSS MORE
COMPLICATED COVARIANCE KERNELS, MULTIPLE KERNELS, etc.  MODEL
CHECKING.}

@@

\bibitem[Walker et al.(2015)]{walker15} Walker, M.~G., 
Olszewski, E.~W., \& Mateo, M.\ 2015, \mnras, 448, 2717
